### 2016-08-28 paper.tex
Fix cross-reference to tow tank picture

Measurements were conducted in the UNH tow/wave tank, pictured in
Fig.~\ref{fig:exp-setup}, a 36 m long facility with a 3.66 m wide by 2.44 m deep
cross-section, capable of tow speeds up to 3 m/s. The blockage ratio based on
the rotor frontal and tank cross-sectional area was 10\%. The turbine was
mounted in a frame built from NACA 0020 struts, attached to the tow carriage by
four linear bearings, which transfer all streamwise force to a pair of 500 lbf
capacity Sentran ZB3 S-beam load cells \cite{SentranZB}. The turbine shaft RPM
was controlled by a servo motor system, which allowed precise control of the
turbine tip speed ratio. The load torque was measured by an Interface T8 200 Nm
capacity inline rotary torque transducer \cite{InterfaceT8}. An additional
Sentran ZB3 load cell mounted at a fixed distance from the servo motor via a
moment arm provided a redundant torque measurement, measurements from which were
nearly identical to the inline transducer, providing additional confidence in
the results. Turbine shaft angle was measured using the Kollmorgen AKD servo
drive's emulated encoder output \cite{KollmorgenAKD}, set to $10^5$ counts per
turbine shaft revolution. Carriage speed, and therefore inflow velocity was
measured using a Renishaw LM15 linear encoder with 10 $\mu$m resolution
\cite{RenishawLM15}. All of these performance-related quantities were sampled at
2 kHz, while the tow tank's motion controller provided redundant measurements of
the carriage speed turbine angular velocity sampled at 1 kHz. Turbine wake
measurements at 1 meter downstream were measured with a Nortek Vectrino+
acoustic Doppler velocimeter \cite{NortekVectrino}, sampling at 200 Hz. A photo
and drawing of the experimental setup are shown in
Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.

>>>>

Measurements were conducted in the UNH tow/wave tank, pictured in
Fig.~\ref{fig:exp-setup-photo}, a 36 m long facility with a 3.66 m wide by 2.44
m deep cross-section, capable of tow speeds up to 3 m/s. The blockage ratio
based on the rotor frontal and tank cross-sectional area was 10\%. The turbine
was mounted in a frame built from NACA 0020 struts, attached to the tow carriage
by four linear bearings, which transfer all streamwise force to a pair of 500
lbf capacity Sentran ZB3 S-beam load cells \cite{SentranZB}. The turbine shaft
RPM was controlled by a servo motor system, which allowed precise control of the
turbine tip speed ratio. The load torque was measured by an Interface T8 200 Nm
capacity inline rotary torque transducer \cite{InterfaceT8}. An additional
Sentran ZB3 load cell mounted at a fixed distance from the servo motor via a
moment arm provided a redundant torque measurement, measurements from which were
nearly identical to the inline transducer, providing additional confidence in
the results. Turbine shaft angle was measured using the Kollmorgen AKD servo
drive's emulated encoder output \cite{KollmorgenAKD}, set to $10^5$ counts per
turbine shaft revolution. Carriage speed, and therefore inflow velocity was
measured using a Renishaw LM15 linear encoder with 10 $\mu$m resolution
\cite{RenishawLM15}. All of these performance-related quantities were sampled at
2 kHz, while the tow tank's motion controller provided redundant measurements of
the carriage speed turbine angular velocity sampled at 1 kHz. Turbine wake
measurements at 1 meter downstream were measured with a Nortek Vectrino+
acoustic Doppler velocimeter \cite{NortekVectrino}, sampling at 200 Hz. A photo
and drawing of the experimental setup are shown in
Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.
